%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   Hi, All
%   Arun Xavier, VAST Thrissur
%
%   for more  Visit my Page - http://arunxeee.blogspot.in/
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%
\chapter*{\centering Acknowledgement}
%


\par
\hspace{0.9cm}
\vspace {.2cm}
\par
\hspace{.35cm}I would like to thank the Lord Almighty, the foundation of all wisdom who has been guiding us in every step. I wish to record my indebtedness and thankfulness to all who helped me to prepare this design project titled {\bf \vtitle} and present it in a satisfactory way. This report is part of my work related to the paper CS 341 DESIGN PROJECT 
\vspace{0.2cm}
\par
\hspace{0.35cm}My sincere thanks to {\bf \vprincipal}, Principal, for providing me all the necessary facilities. I take this opportunity to extend my thanks to {\bf \vhod} the Head of {\bf \vdept} for giving me valuable guidance in developing this project. I'm extremely thankful to my guides and supervisors {\bf \vguide}, Asst.Professor, {\bf Ms. Remya P.S}, Asst.Professor in the Department of {\bf \vdept} for giving me valuable suggestions and critical inputs in the preparation of this report. 
\vspace{.2cm}
\par 
\hspace{.35cm}I express my heartfelt thanks to the {\bf Lab Instructors} for their valuable support and assistance for my work. My sincere thanks to {\bf parents and friends} who have helped me during the course of the project work and made it a great success.

\begin{flushright}
{\vauthora}\\
{\vauthorb}\\
{\vauthorc}

\vclass\  (\vadmissionyear\  Admissions)\\
Vidya Academy of Science \& Technology\\
\vdate  \hfill Thrissur - 680 501.
\end{flushright}